Scientific Reports Title to see here (20 words or less)

### 2016-06-23 draft1.tex
changed single objective sensitivity table

\subsection*{Sensitivity Using Finite Differences}
The derivatives of all parameters were estimated using central differences. 
\begin{equation}
\frac{dh}{d\theta_j} = \frac{h(\theta_0+\frac{e_j}{2})-h(\theta_0-\frac{e_j}{2})}{\delta}
\end{equation}
where $\delta=10^{-8}*\theta_j$ and $e_j$ is a vector of length $\delta$ in the $j^{th}$ direction.
To collapse the time dimension, we calculated overall state sensitivity coefficients. \cite{stelling2004robustness}
\begin{equation}
S_{0j}(t) = \frac{1}{n_s}p_j \left(\sum_{k=1}^{n_t} \sum_{i=1}^{n_s} \left[ \frac{1}{x_i} \frac{dx_i(t_k)}{dp_j} \right]^2 \right)^{1/2}
\end{equation}
where $n_s$ = 1, as $h$ is the only state variable and $n_t$ is the number of time points available for that patient.
From the original values provided by Olufsen and Ottesen, we found that $h_0$ was the most sensitive parameter, followed by $N$, $m_{ach}$, and $m_{nor}$ in that order. Of the four most sensitive equations, three of them ($h_0$, $m_{ach}$ and $m_{nor}$) appear directly in the equation for heart rate, and $N$ indirectly appears, as both $c_{ach}$ and $c_{nor}$ are functions of $N$.
The four parameters that were the most sensitive in our study were among the five most sensitive parameters found by Olufsen and Ottesen, as seen in \ref{tab:OSSCsoriginalParams}.
With the new best parameters, the same four parameters are the most sensitive, as shown in \ref{tab:clusterSensitivity}. 
For the multiobjective case, we used the same finite differences, but averaged them not only over the patients, but over the families of parameters-the ten best for each cluster. As with the single objective case, $h_0$ is the most sensitive parameter, followed by $N$, as seen in \ref{fig:MultiobjectiveSensitivityGraph}.
\section*{Discussion}
The Discussion should be succinct and must not contain subheadings.
\section*{Methods}
All calculations were carried out Ubunutu 16.04 using Julia version .0.4.5, with 7.7 GB of available RAM on a Intel Core i7-6700 CPU @ 3.40GHz. Differential equations were solved using the ODE package, with solvers ode23 and ode78, with an absolute and relative tolerance of $10^{-8}$. 
\bibliography{draft1}
\section*{Acknowledgements (not compulsory)}
Acknowledgements should be brief, and should not include thanks to anonymous referees and editors, or effusive comments. Grant or contribution numbers may be acknowledged.
\section*{Author contributions statement}
Must include all authors, identified by initials, for example:
A.A. conceived the experiment(s),  A.A. and B.A. conducted the experiment(s), C.A. and D.A. analysed the results.  All authors reviewed the manuscript. 
\section*{Additional information}
To include, in this order: \textbf{Accession codes} (where applicable); \textbf{Competing financial interests} (mandatory statement). 
The corresponding author is responsible for submitting a \href{http://www.nature.com/srep/policies/index.html#competing}{competing financial interests statement} on behalf of all authors of the paper. This statement must be included in the submitted article file.

@@

\begin{table}[h]
\centering
\caption{Average Overall State Sensitivity Coefficents Using Original Parameters}
\label{tab:OSSCsoriginalParams}
\begin{tabular}{lllllllll}
$\frac{dh}{dN}$    & $\frac{dh}{dk_1}$  & $\frac{dh}{d\tau_1}$ & $\frac{dh}{d\tau_2}$ &$\frac{dh}{d\tau_{ach}}$ & $\frac{dh}{d\tau_{nor}}$ & $\frac{dh}{dh_0}$   & $\frac{dh}{dm_{nor}}$ & $\frac{dh}{dm_{ach}}$ \\
15.3620 & 0.0792 & 0.0740  & 0.0156  & 0.0540   & 0.0006    & 19.9294 & 0.5740  & 14.5868
\end{tabular}
\end{table} 
%\begin{table}[]
%\centering
%\caption{Sensitivity by clusters}
%\label{tab:clusterSensitivity}
%\begin{tabular}{|l|l|l|l|l|l|l|l|l|l|}
%\hline
%Cluster   & $\frac{dh}{dN}$ & $\frac{dh}{k_1}$ & $\frac{dh}{\tau_1}$ & $\frac{dh}{tau_2}$ & $\frac{dh}{\tau_{ach}}$ & $\frac{dh}{\tau_{nor}}$ & $\frac{dh}{h0}$ & $\frac{dh}{m_{nor}}$ & $\frac{dh}{m_{ach}}$ \\ \hline
%Overall   & 4.8352          & 0.2500           & 0.5088              & 0.0033             & 0.0204                  & 0.5720                  & 19.9294         & 1.1339               & 4.4651               \\ \hline
%cluster 1 & 4.7152          & 0.2456           & 0.5027              & 0.0033             & 0.0201                  & 0.5755                  & 19.4780         & 1.1438               & 4.3593               \\ \hline
%cluster 2 & 4.9137          & 0.2528           & 0.5128              & 0.0033             & 0.0206                  & 0.5697                  & 20.2248         & 1.1275               & 4.5344               \\ \hline
%\end{tabular}
%\end{table}
\end{document}

>>>>

\subsection*{Sensitivity Using Finite Differences}
The derivatives of all parameters were estimated using central differences. 
\begin{equation}
\frac{dh}{d\theta_j} = \frac{h(\theta_0+\frac{e_j}{2})-h(\theta_0-\frac{e_j}{2})}{\delta}
\end{equation}
where $\delta=10^{-8}*\theta_j$ and $e_j$ is a vector of length $\delta$ in the $j^{th}$ direction.
To collapse the time dimension, we calculated overall state sensitivity coefficients. \cite{stelling2004robustness}
\begin{equation}
S_{0j}(t) = \frac{1}{n_s}p_j \left(\sum_{k=1}^{n_t} \sum_{i=1}^{n_s} \left[ \frac{1}{x_i} \frac{dx_i(t_k)}{dp_j} \right]^2 \right)^{1/2}
\end{equation}
where $n_s$ = 1, as $h$ is the only state variable and $n_t$ is the number of time points available for that patient. We calculated sensitivites of parameters that were optimized and not that of those held constant.
\subsubsection*{Single Objective Sensitivity}
From the original values provided by Olufsen and Ottesen, we found that $h_0$ was the most sensitive parameter, followed by $N$, $m_{ach}$, and $m_{nor}$ in that order. Of the four most sensitive equations, three of them ($h_0$, $m_{ach}$ and $m_{nor}$) appear directly in the equation for heart rate, and $N$ indirectly appears, as both $c_{ach}$ and $c_{nor}$ are functions of $N$.
The four parameters that were the most sensitive in our study were among the five most sensitive parameters found by Olufsen and Ottesen, as seen in \ref{tab:OSSCsoriginalParams}.
\subsubsection*{Multiobjective Sensitivity} 
For the multiobjective case, we used the same finite differences, but averaged them not only over the patients, but over the families of parameters-the ten best for each cluster. As with the single objective case, $h_0$ is the most sensitive parameter, followed by $N$, as seen in \ref{fig:MultiobjectiveSensitivityGraph}.
\section*{Discussion}
The Discussion should be succinct and must not contain subheadings.
\section*{Methods}
All calculations were carried out Ubunutu 16.04 using Julia version .0.4.5, with 7.7 GB of available RAM on a Intel Core i7-6700 CPU @ 3.40GHz. Differential equations were solved using the ODE package, with solvers ode23 and ode78, with an absolute and relative tolerance of $10^{-8}$. 
\bibliography{draft1}
\section*{Acknowledgements (not compulsory)}
Acknowledgements should be brief, and should not include thanks to anonymous referees and editors, or effusive comments. Grant or contribution numbers may be acknowledged.
\section*{Author contributions statement}
Must include all authors, identified by initials, for example:
A.A. conceived the experiment(s),  A.A. and B.A. conducted the experiment(s), C.A. and D.A. analysed the results.  All authors reviewed the manuscript. 
\section*{Additional information}
To include, in this order: \textbf{Accession codes} (where applicable); \textbf{Competing financial interests} (mandatory statement). 
The corresponding author is responsible for submitting a \href{http://www.nature.com/srep/policies/index.html#competing}{competing financial interests statement} on behalf of all authors of the paper. This statement must be included in the submitted article file.

@@

\begin{table}[h]
\centering
\caption{Average Overall State Sensitivity Coefficents For Single Objective Case}
\label{tab:OSSCsoriginalParams}
\begin{tabular}{|l|l|l|l|l|l|l|l|l|l|}
\hline
Parameter set        & $S_{N}$    & $S_{k_1}$ & $S_{\tau_1}$ & $S_{\tau_2}$ & $S_{\tau_{ach}}$ & $S_{\tau_{nor}}$ & $S_{h_0}$   & $S_{m_{ach}}$ & $S_{m_{nor}}$ \\ \hline
original parameters  &            &           &              &              &                  &                  &             &               &                \\ \hline
estimated parameters & $1.75\pm4$ & $.76\pm3$ & $.87\pm3$    & $.39\pm2$    & $0.31\pm1.8$     & $4.18\pm1.5$     & $19.9\pm 6$ & $6.69\pm2$    & $.76\pm 1.8$   \\ \hline
\end{tabular}
\end{table} 
%\begin{table}[]
%\centering
%\caption{Sensitivity by clusters}
%\label{tab:clusterSensitivity}
%\begin{tabular}{|l|l|l|l|l|l|l|l|l|l|}
%\hline
%Cluster   & $\frac{dh}{dN}$ & $\frac{dh}{k_1}$ & $\frac{dh}{\tau_1}$ & $\frac{dh}{tau_2}$ & $\frac{dh}{\tau_{ach}}$ & $\frac{dh}{\tau_{nor}}$ & $\frac{dh}{h0}$ & $\frac{dh}{m_{nor}}$ & $\frac{dh}{m_{ach}}$ \\ \hline
%Overall   & 4.8352          & 0.2500           & 0.5088              & 0.0033             & 0.0204                  & 0.5720                  & 19.9294         & 1.1339               & 4.4651               \\ \hline
%cluster 1 & 4.7152          & 0.2456           & 0.5027              & 0.0033             & 0.0201                  & 0.5755                  & 19.4780         & 1.1438               & 4.3593               \\ \hline
%cluster 2 & 4.9137          & 0.2528           & 0.5128              & 0.0033             & 0.0206                  & 0.5697                  & 20.2248         & 1.1275               & 4.5344               \\ \hline
%\end{tabular}
%\end{table}
\end{document}
